Tables

### 2019-11-05 code/figures.rmd
Updated figure text to match
updated main rma function for ML2 + figure 3

fisher_fit <- function(x){
    fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
    }

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(effect_type == "Raw mean difference" & !outcomes1_2 == "mean _ SE") %>% #No method in metafor to compute SMD when standard deviations not given, so skip this study 
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect")

fisher <- dat %>% 
  filter(effect_type == "r") %>% 
  split(.$effect) %>% 
  map_dfr(fisher_fit, .id = "effect")

#effects that were transformed from OR to SMD by ML1 which we will drop
OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(OR2d, MD_standardized$effect, fisher$effect)) %>% #drop old SMD converted OR, unstandardized MD and raw correlations
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(fisher) %>% #add correlations as fisher's z
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% fisher$effect, "Fisher's z", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Fisher's z"))

@@

Figure 3. The correlation between effect size and A) tau2, b) I2 and c) H2 respectively  22 effects that were measured as mean or standardized mean differences and 6 effects measured as correlations from ten pre-registered multi-lab replication projects. Effects reported as mean differences were standardized and correlations were transformed into Fisher’s z. Shaded bands represent 95% confidence intervals

>>>>

OR_fit <- function(x){
    fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
}

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE study since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect")

#effects that were originally transformed from OR to SMD by ML1 which we refit as OR
OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 
           'Norm of reciprocity', 'Low vs. high category scales')

ml2_or <- c("Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2") #odds ratio effects in ML2 we will fit as OR

odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or)) %>% 
  split(.$effect) %>% 
  map_dfr(OR_fit, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(odds_ratios) %>% #add odds ratios
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% odds_ratios$effect, "Odds Ratio", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Odds Ratio"))

@@

Figure 3. The correlation between effect size and A) tau2, B) I2 and C) H2 respectively  40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios from 13 pre-registered multi-lab replication projects. Effects reported as mean differences were standardized. Square brackets contain 95% bootstrapped percentile confidence intervals.

### 2019-11-05 code/tables.rmd
updated main rma function for ML2 + figure 3

#Shortened version of APA reference
papers <- c('Klein et al. (2014)', 
'Ebersole et al. (2016)',
'Alogna et al. (2014)',
'Alogna et al. (2014)',
'Eerland et al. (2016)',
'Hagger et al. (2016)',
'Cheung et al. (2016)',
'Wagenmakers et al. (2016)',
'Bouwmeester et al. (2017)',
"O'Donnell et al. (2017)")

##Full APA reference below
# c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahn?k, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project. Social Psychology, 45(3), 142-152.', 
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarrac?n (2011). Perspectives on Psychological Science, 11(1), 158-171.',
# 'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect. Perspectives on Psychological Science, 11(4), 546-573.',
# 'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahn?k, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002). Perspectives on Psychological Science, 11(5), 750-764.',
# 'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988). Perspectives on Psychological Science, 11(6), 917-928.',
# 'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., B?gue, L., Bra?as-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012). Perspectives on Psychological Science, 12(3), 527-542.',
# "O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998). The relation between perception and behavior, or how to win a game of trivial pursuit. Journal of personality and social psychology. Perspectives on Psychological Science."

description <- c("Two correlational effects: 'Gender math attitude' compared implicit attitudes (IAT) towards math between genders and 'IAT correlation math' correlated implicit attitudes with self-reported measures. The remainder were experiments with two independent groups. The groups were primed in some way (Anchoring 1-4; low vs. high category scales; norm of reciprocity; flag priming; currency priming), asked to imagine slightly different situations (Sunk costs; gain vs. loss framing; gambler's fallacy; imagined contact) or asked their agreement with statements presented differently (Allowed vs. forbidden; quote attribution). ", #ML1
            "Several effects were experiments with two independent groups. The groups were either primed in some way (Power and perspective; warmth perceptions; subjective distance interaction), saw slightly different statements (Elaboration likelihood interaction; credentials interaction) or experienced different situations (weight embodiment). Examined interactions were between treatment conditions and participant characteristics. One priming effect (metaphor) compared two treatment groups with a control. One effect was correlational: 'Conscientiousness and persistence' was measured by an unsolvable anagram task and self-report respectively. The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
                 "Verbal overshadowing 1; Independent two-group experiment. Participants either described a robber after watching a video or listed countries/capitals and after a filler task attempted to identify the robber in a lineup.", #RRR1
            "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
                 "Grammar's effect on interpretation; Independent two-group vignette experiment with three outcome variables. Participants read about actions either described in imperfect or perfect tense and then rated protagonist's intentions (intentionality/intention attribution/detailed processing).", #RRR3
            "Ego depletion; Independent two-group experiment. Participants either assigned to a cognitively demanding task or a neutral, and performance was then measured in a subsequent cognitive task.", #RRR4
            "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' by holding a pen in their mouth differently and simultaneously rated funniness of cartoons. ", #RRR6
            "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8

@@

sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed. 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
                     "31/32 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR1
                     "22/23 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR2
                     "11/12 samples were undergraduate students mostly aged 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                     "All samples consisted of in-lab undergraduate students", #RRR4
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR5
               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
               'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
                     "All samples consisted of in-lab undergraduate students aged 18-25") #RRR8

>>>>

#Shortened version of APA reference
papers <- c('Klein et al. (2014)', 
            'Klein et al. (2018)',
'Ebersole et al. (2016)',
'Alogna et al. (2014)',
'Alogna et al. (2014)',
'Eerland et al. (2016)',
'Hagger et al. (2016)',
'Cheung et al. (2016)',
'Wagenmakers et al. (2016)',
'Bouwmeester et al. (2017)',
"O'Donnell et al. (2017)")

##Full APA reference below
# c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahn?k, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project. Social Psychology, 45(3), 142-152.', 
# Add full APA ref for ML2
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarrac?n (2011). Perspectives on Psychological Science, 11(1), 158-171.',
# 'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect. Perspectives on Psychological Science, 11(4), 546-573.',
# 'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahn?k, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002). Perspectives on Psychological Science, 11(5), 750-764.',
# 'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988). Perspectives on Psychological Science, 11(6), 917-928.',
# 'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., B?gue, L., Bra?as-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012). Perspectives on Psychological Science, 12(3), 527-542.',
# "O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998). The relation between perception and behavior, or how to win a game of trivial pursuit. Journal of personality and social psychology. Perspectives on Psychological Science."

description <- c("Two correlational effects: 'Gender math attitude' compared implicit attitudes (IAT) towards math between genders and 'IAT correlation math' correlated implicit attitudes with self-reported measures. The remainder were experiments with two independent groups. The groups were primed in some way (Anchoring 1-4; low vs. high category scales; norm of reciprocity; flag priming; currency priming), asked to imagine slightly different situations (Sunk costs; gain vs. loss framing; gambler's fallacy; imagined contact) or asked their agreement with statements presented differently (Allowed vs. forbidden; quote attribution). ", #ML1
                 "'Summary about ML2 effects': 17/28 effects were experiments with two independent groups. Two correlational effects. Two difference between correlations. 4 odds ratio effects. One hierarchical regression effect. One strange effect.", #ML2
            "Several effects were experiments with two independent groups. The groups were either primed in some way (Power and perspective; warmth perceptions; subjective distance interaction), saw slightly different statements (Elaboration likelihood interaction; credentials interaction) or experienced different situations (weight embodiment). Examined interactions were between treatment conditions and participant characteristics. One priming effect (metaphor) compared two treatment groups with a control. One effect was correlational: 'Conscientiousness and persistence' was measured by an unsolvable anagram task and self-report respectively. The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML3
                 "Verbal overshadowing 1; Independent two-group experiment. Participants either described a robber after watching a video or listed countries/capitals and after a filler task attempted to identify the robber in a lineup.", #RRR1
            "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
                 "Grammar's effect on interpretation; Independent two-group vignette experiment with three outcome variables. Participants read about actions either described in imperfect or perfect tense and then rated protagonist's intentions (intentionality/intention attribution/detailed processing).", #RRR3
            "Ego depletion; Independent two-group experiment. Participants either assigned to a cognitively demanding task or a neutral, and performance was then measured in a subsequent cognitive task.", #RRR4
            "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' by holding a pen in their mouth differently and simultaneously rated funniness of cartoons. ", #RRR6
            "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8

@@

sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed. 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
                     "'ML2 sample information'", #ML2
                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
                     "31/32 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR1
                     "22/23 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR2
                     "11/12 samples were undergraduate students mostly aged 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                     "All samples consisted of in-lab undergraduate students", #RRR4
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR5
               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
               'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
                     "All samples consisted of in-lab undergraduate students aged 18-25") #RRR8
